Long-term trends in the contribution of major causes of death to the black-white life expectancy gap by US state. A retrospective study of all deaths between 1969 and 2013

### 2017-06-29 Code/4_combined-meta-regression.Rmd
cubic splines because we live in a curvy world!

#run 12 stratified models. bs() created the b-spline basis
RE.models <- cod_decomp_results %>% 
  group_by(COD, sex) %>%
  do(fit = lmer(COD_cont_yrs_mean ~ bs(year, degree = 1, df = 5) + (1|state),
              weights = 1/(COD_cont_yrs_SE)^2, 
              data = .))

@@

#run 12 stratified models. bs() created the b-spline basis
models <- cod_decomp_results %>% 
  group_by(COD, sex) %>%
  do(fit = lm(COD_cont_yrs_mean ~ bs(year, degree = 1, df = 5) + state,
              weights = 1/(COD_cont_yrs_SE)^2, 
              data = .))

@@

```{r RE_meta_regression_agecod_infants_only, echo = F}
RE.models.infants <- age_cod_results_infants_AOC %>% 
  group_by(sex) %>%
  do(fit = lmer(age_COD_cont_yrs_mean ~ bs(year, degree = 1, df = 5) + (1|state),
              weights = 1/(age_COD_cont_yrs_SE)^2, 
              data = .))

@@

```{r save_data}
write.csv(cod_decomp_results, "./Results2/cod_decomp_results.csv")

write.csv(age_cod_results_infants_AOC, "./Results2/age_cod_results_infants_AOC.csv")
```

>>>>

#run 12 stratified models. bs() created the b-spline basis
RE.models <- cod_decomp_results %>% 
  group_by(COD, sex) %>%
  do(fit = lmer(COD_cont_yrs_mean ~ bs(year, degree = 3, knots = c(1980, 1991, 2002)) + (1|state),
              weights = 1/(COD_cont_yrs_SE)^2, 
              data = .))

@@

#run 12 stratified models. bs() created the b-spline basis
models <- cod_decomp_results %>% 
  group_by(COD, sex) %>%
  do(fit = lm(COD_cont_yrs_mean ~ bs(year, degree = 3, knots = c(1980, 1991, 2002)) + state,
              weights = 1/(COD_cont_yrs_SE)^2, 
              data = .))

@@

```{r RE_meta_regression_agecod_infants_only, echo = F}
RE.models.infants <- age_cod_results_infants_AOC %>% 
  group_by(sex) %>%
  do(fit = lmer(age_COD_cont_yrs_mean ~ bs(year, degree = 3, df = 7) + (1|state),
              weights = 1/(age_COD_cont_yrs_SE)^2, 
              data = .))

@@

```{r save_data}
write.csv(cod_decomp_results, "./Results2/cod_decomp_results_cubic.csv")

write.csv(age_cod_results_infants_AOC, "./Results2/age_cod_results_infants_AOC_cubic.csv")
```

### 2017-06-29 Manuscript/Manuscript_COD_Trends_BMJOpen.Rmd
cubic splines because we live in a curvy world!

source("./Code/life_expectancy_functions.R")
```

```{r load_data, echo=F}
BlackWhite_results <- read.csv("./Results2/BlackWhite_results.csv")
BlackWhite_results <- reorder.as.map2(BlackWhite_results, "state", "stabbrs")
cod_decomp_results <- read.csv("./Results2/cod_decomp_results.csv")
cod_decomp_results <- reorder.as.map2(cod_decomp_results, "state", "stabbrs")
cod_decomp_results$COD_rev <- factor(cod_decomp_results$COD, levels = c("Cardiovascular", "Cancers", "All other causes",
                                                                        "Communicable", "Non-communicable",  "Injuries"))

age_cod_results_infants_AOC <- read.csv("./Results2/age_cod_results_infants_AOC.csv")
age_cod_results_infants_AOC$stabbrs <- state.abb[match(age_cod_results_infants_AOC$state, state.name)]
age_cod_results_infants_AOC$stabbrs[age_cod_results_infants_AOC$state == "Washington DC"] <- "DC"
age_cod_results_infants_AOC <- reorder.as.map2(age_cod_results_infants_AOC, "state", "stabbrs")

@@

```{r plotting_resid_fx, echo = F}
plot.resid.trends <- function(dataset, COD1, sex1) {
  subset.data <- subset(dataset, COD == COD1 & sex == sex1)
  subset.data$order <- reorder(subset.data$state, subset.data$sum.residual, first)

@@

```{r create-the-resid-plots, echo = F, message = F}
for(COD_i in levels(cod_decomp_results$COD)) {
  for(sex_i in levels(cod_decomp_results$sex)) {
    assign(paste0(COD_i, ".", sex_i, ".plot"), plot.resid.trends(dataset = cod_decomp_results, 
                                                                         COD1 = COD_i, sex1 = sex_i))
  }
}
```

>>>>

source("../Code/life_expectancy_functions.R")
```

```{r load_data, echo=F}
BlackWhite_results <- read.csv("../Results2/BlackWhite_results.csv")
BlackWhite_results <- reorder.as.map2(BlackWhite_results, "state", "stabbrs")
cod_decomp_results <- read.csv("../Results2/cod_decomp_results_cubic.csv")
cod_decomp_results <- reorder.as.map2(cod_decomp_results, "state", "stabbrs")
cod_decomp_results$COD_rev <- factor(cod_decomp_results$COD, levels = c("Cardiovascular", "Cancers", "All other causes",
                                                                        "Communicable", "Non-communicable",  "Injuries"))

age_cod_results_infants_AOC <- read.csv("../Results2/age_cod_results_infants_AOC_cubic.csv")
age_cod_results_infants_AOC$stabbrs <- state.abb[match(age_cod_results_infants_AOC$state, state.name)]
age_cod_results_infants_AOC$stabbrs[age_cod_results_infants_AOC$state == "Washington DC"] <- "DC"
age_cod_results_infants_AOC <- reorder.as.map2(age_cod_results_infants_AOC, "state", "stabbrs")

@@

```{r plotting_contributions_fx, echo = F}
plot.contribution.trends <- function(dataset, COD1, sex1) {
  subset.data <- subset(dataset, COD == COD1 & sex == sex1)
  subset.data$order <- reorder(subset.data$state, subset.data$sum.residual, first)

@@

```{r create-the-resid-plots, echo = F, message = F}
for(COD_i in levels(cod_decomp_results$COD)) {
  for(sex_i in levels(cod_decomp_results$sex)) {
    assign(paste0(COD_i, ".", sex_i, ".plot"), plot.contribution.trends(dataset = cod_decomp_results, 
                                                                         COD1 = COD_i, sex1 = sex_i))
  }
}
```
